PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-21 paper.tex
Update on Overleaf.
CoRL template, updated pictures, started restructuring

\documentclass[a4paper]{IEEEconf}

@@

\author{Séverin Lemaignan, Tony Belpaeme}

@@

\section{Machine learning and social behaviour}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{setup.png}
    \caption{The free play social interactions sandbox\todo[inline]{replace with a
    cihld-child configuration}}
    \label{fig|setup}
\end{figure}

@@

\paragraph{From unstructured to structured play}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{sandbox}
    \caption{Example of a game situation: the child and the robot `build'
    together a zoo. The animals and the blocks can be dragged over the whole
    play area, while the background picture is static and purely decorative.}
    \label{fig|sandbox}
\end{figure}

\paragraph{Pretence}

\begin{figure}
    \centering
    \includegraphics[width=0.7\linewidth]{sandbox-release-cheetah}
    \caption{Possible play situation: the children pretend to release the cheetah
    and create a story where the cheetah scares away the visitors.}
    \label{}
\end{figure}

@@

Figure~\ref{fig|architecture} presents the software architecture of the sandbox.

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{freeplay-sandbox-architecture}
\label{fig|architecture}
\caption{Architecture of the free play sandbox. Yellow nodes represent
    hardware (cameras and robot); purple nodes relate to the game interface;
    red nodes manage the robot; the green node implements the game policy (when
    the robot is playing); blue nodes relates to visual attention tracking.}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{rviz-sandtray}
    \caption{The freeplay sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.
    visualisation tool.}
    \label{fig|rviz}
\end{figure}

@@

@@

\subsection{Initial Dataset Analysis}

@@

@@

\bibliographystyle{plain}
\bibliography{biblio}

>>>>

\documentclass{article}

\usepackage{corl_2017}

@@

\author{Séverin Lemaignan, Charlotte Edmunds, Tony Belpaeme}

@@

\subsection{Machine learning and social behaviour}

@@

analysis of behavioural alignment between partners (via
metrics like the recently proposed \emph{Individual Motor
Signature}~\cite{slowinski2016dynamic})

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\linewidth]{setup-child-child.png}
    \hspace{1em}
    \includegraphics[width=0.4\linewidth]{setup-child-robot.png}
    \caption{The free play social interactions sandbox. Data acquisition is
    performed under two (between subjets) conditions: either children playing together, or one
    child playing with a \emph{non-social} robot.}
    \label{fig|setup}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{sandbox}
    \caption{Example of a game situation: the child and the robot `build'
    together a zoo. Items (animals, characters...) can be dragged over the whole
    play area, while the background picture can be painted over.}
    \label{fig|sandbox}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{rviz-sandtray}
    \caption{The freeplay sandbox, viewed at runtime within ROS RViz. The
    current background drawing is published on a regular image
    topic and computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.}
    \label{fig|rviz}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{3d-point-cloud-facial-features}
    \caption{The freeplay sandbox, viewed at runtime within ROS RViz. The
    current background drawing (bottom left) is published on a regular image
    topic. Simple computer vision is used to segment it into zones (visible in
    the central panel). The poses and bounding boxes of the interactive items
    are published as well, and turned into an occupancy map, used to plan the
    robot's arm motion.
    visualisation tool.}
    \label{fig|rviz}
\end{figure}

\subsection{Conditions}\label{conditions}

\begin{itemize}
\item
  Condition A: one pair of children freely play together on the
  sandtray.
\item
  Condition B: one child play together with the robot, the robot does
  not exhibit any social behaviour.
\end{itemize}

\subsection{Demographics}\label{demographics}

\begin{itemize}
\item
  Condition A: 40 pairs of children (ie, 80 children)
\item
  Condition B: 40 children
\end{itemize}

2 age groups, balanced across conditions: 4 y.o. (nursery) and 6 to 7
y.o. (Y1/Y2)

Normally developping children, from local primary schools and nurseries.

\subsection{Experimental Setup}\label{experimental-setup}

On large touchscreen, mounted on a horizontal frame (\emph{sandtray});
both children (condition A, Figure 2) or the child and the robot
(condition B, Figure 3) are facing each other.

\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.4\linewidth]{setup_child_child_top}
    \hspace{1.5cm}
    \includegraphics[width=0.4\linewidth]{setup_child_robot_top}
    \caption{Experimental setup, child-child condition (left) and child-robot
    condition (right).}
\end{figure}

The experimenter stays in the room, visible from the child. When
requested by the nursery or school, another childminder (nursery/school
staff) can be present in the room. She/he is however asked not to step
in during the experiment.

The interaction is recorded by 3 cameras (on `environment' camera
filming the whole scene; two RGB-D cameras, focused on each of the
children faces).

Audio is recorded as well with 2 microphones integrated to the RGB-D
cameras.

One computer (integrated with the touchscreen) manages the game and the
synchronous recording of the cameras and microphones.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  welcome (5 min):

  \begin{itemize}
  \item
    place children on cushions
  \item
    give them the yellow/purple sport bibs
  \item
    make sure hairs are tied (to help with face tracking)
  \item
    ask names (but do not write them down)
  \item
    fill up questionaire on the tablet -- age, gender, familiarity with
    tablet
  \item
    \textbf{remind the children that they can withdraw at anytime}
  \item
    \textbf{explain the purpose of the study: showing robots how
    children play}
  \item
    in condition B, present briefly the robot -- saying it is not a very
    sociable robot, and it might play alone.
  \end{itemize}
\item
  visual focus task (30 seconds)
\item
  tutorial (1-2 min): explain how to interact with the game, ensure the
  children are confident with the manipulation/drawing
\item
  main freeplay task (up to 40 min):

  \begin{itemize}
  \item
    start the recording
  \item
    example prompt: ``I let you play now! You can build a zoo, or tell
    stories, as you want''
  \item
    let children play
  \item
    encourage children to keep playing at least 5 min
  \item
    once they wish to stop, stop recording
  \end{itemize}
\item
  debriefing (5 min):

  \begin{itemize}
  \item
    answer possible questions from the children
  \item
    give stickers
  \end{itemize}
\end{enumerate}

Total duration: 30 minutes per group.
\subsection{Initial Dataset Analysis}

@@

\section{Discussion}

@@

\bibliography{biblio}
